Light inextensible strings under tension in the Schwarzschild geometry

### 2019-08-28 string_physics_teacher.tex
more terse

\noindent
{\tt
Needs["VariationalMethods`"]\\
p = EulerEquations[Sqrt[y'[x]\^{}2/(1-1/y[x]) + y[x]\^{}2],y[x],x] // FullSimplify\\
ss = p[[1]]//Numerator\\
DSolve[ss==0,y[x],x]
}}, an expression for the second derivative of~$r$:

>>>>

\noindent
{\tt
Needs["VariationalMethods`"]\\
p = EulerEquations[Sqrt[y'[x]\^{}2/(1-1/y[x]) + y[x]\^{}2],y[x],x] // FullSimplify\\
DSolve[p[[1]]//Numerator == 0, y[x],x]
}}, an expression for the second derivative of~$r$:
